\vspace{-\topskip}
\section{Experience}
\subsection{Davis Selected Advisers}
\vspace{1ex}
\begin{minipage}[t]{0.245\textwidth}
    \vspace{-\topskip}
    {\hspace{.25em}}\footnotesize\textsf{\DTMdisplaydate{2022}{04}{11}{}--current}
\end{minipage}
\hfill
\begin{minipage}[t]{0.75\textwidth}
    \vspace{-\topskip}
    {\scshape\textsf{Database Administrator}
    }\\
    \setlength{\parskip}{0.7em}
    \setlength{\baselineskip}{2.6ex}

    Established and maintain a centralized PowerShell library of functions and
    classes for use across Davis-internal scripts.

    Coordinate SQL Server installation, upgrades, and migrations, in standalone
    and clustered instances.

    Analyze and enhance existing procedures and scripts for
    robustness, flexibility, and adaptability.

    Design flexible scripts and procedures in support of internal and
    third-party databases and applications.


    {
}
\end{minipage}
\vspace{0ex}

\subsection{Intuit Inc}
\experienceitem
    {Support Operations Analyst, Seasonal}
    {2021}{11}{15}
    {2022}{04}{01}
    {
        Built tools with Power Query in Excel to improve monthly and continuous
        reviews.

}

\subsection{Celestica Inc}
\experienceitem
    {Supply Chain Analyst, Temporary
    }
    {2021}{08}{30}
    {2021}{11}{05}{

    Built a KPI tracking tool with Google Apps Script (JavaScript), replacing
    heavily-manual daily processes.
    }

\subsection{Fiji Water}
\experienceitem
    {Distribution Associate, Temporary
    }
    {2021}{05}{12}
    {2021}{08}{20}{

    Tracked and reported inbound shipments to various remote
    warehouses, ensuring accurate categorization of inventory.

    Reconciled internal inventory records with warehouse reports.
}



\subsection{Intuit Inc}
\experienceitem{Support Operations Analyst, Seasonal
    }{2020}{03}{23}
     {2020}{12}{11}{

    Supported configuration and testing of inbound call routing.

    Performed ad-hoc reporting of operational performance.
    
    Designed an interactive visualization in R illustrating the flow of
    Intuit's inbound call routing.
    }

\subsection{CyraCom Intl}
\experienceitem{Financial Data Analyst
    }{2016}{01}{22}
     {2020}{01}{15}{

    Owned analysis and reporting of financial and operational business metrics.

    Performed root-cause analyses of metric trends, interpreting data into
    actionable insights.

    Created and maintained recurring reports, implementing automation
    to improve workflow efficiency and accuracy.

    Tailored complex SQL queries to improve workflow and fill reporting gaps.
    
    Built spreadsheet and macro-driven Excel templates, reducing days of work to
    minutes.

    Created and refined a monthly reconciliation process to verify contractor
    payments of $\approx$\$1.5M/month with 100\% accuracy.

    Served as a subject-matter expert to provide insight for CyraCom's language
    needs.
    }

